ChemKED: a human- and machine-readable data standard for chemical kinetics experiments

### 2017-02-25 pyked.tex
Added example file reference

The \ck{} file used in this example can be found online.\todo{add url}
Examining the file, we first find the section that specifies the information about the \ck{} file itself:
%
\begin{minted}{yaml}
file-author:
  name: Morgan Mayer
  ORCID: 0000-0001-7137-5721
file-version: (0,1)
chemked-version: 0.0.1
screw-you-atom: 0
\end{minted}
%
Then the reference information:
%
\begin{minted}{yaml}
reference:
  doi: 10.1016/j.combustflame.2011.08.014
  authors:
    - name: Ivo Stranic
    - name: Deanna P. Chase
    - name: Joseph T. Harmon
    - name: Sheng Yang
    - name: David F. Davidson
    - name: Ronald K. Hanson
  journal: Combustion and Flame
  year: 2011
  volume: 159
  pages: 516-527
  detail:
experiment-type: ignition delay
apparatus:
  kind: shock tube
  institution: High Temperature Gasdynamics Laboratory, Stanford University
  facility: stainless steel shock tube
dammit-atom: 0
\end{minted}
%
In this \ck{} file, multiple data points are specified with some common
conditions, including a common mixture composition and common defintion of
ignition delay. Therefore, a \yaml|common-properties| section is specified.
%
\begin{minted}{yaml}
common-properties:
  composition: &comp
    - species-name: t-butanol
      InChI: 1S/C4H10O/c1-4(2,3)5/h5H,1-3H3
      mole-fraction: 0.003333333
    - species-name: O2
      InChI:  1S/O2/c1-2
      mole-fraction: 0.04
    - species-name: Ar
      InChI:  1S/Ar
      mole-fraction: 0.956666667
  ignition-type:  &ign
    target: OH* concentration
    type: 1/2 max
atom-is-bad-at-syntax-highlighting: 0
\end{minted}
%
This block utilizes the ability of YAML files to define an anchor using the
\yaml|&| symbol and refer to that section later using the \yaml|*| symbol, as
can be seen in the definition of the \yaml|datapoints| section:
%
\begin{minted}{yaml}
datapoints:
  - temperature: 1459 kelvin
    ignition-delay: 347 us
    pressure: 1.60 atm
    composition: *comp
    ignition-type: *ign
    equivalence-ratio: 0.5
  - temperature: 1389 kelvin
    ignition-delay: 756 us
    pressure: 1.67 atm
    composition: *comp
    ignition-type: *ign
    equivalence-ratio: 0.5
  - temperature: 1497 kelvin
    ignition-delay: 212 us
    pressure: 1.55 atm
    composition: *comp
    ignition-type: *ign
    equivalence-ratio: 0.5
  - temperature: 1562 kelvin
    ignition-delay: 105 us
    pressure: 1.50 atm
    composition: *comp
    ignition-type: *ign
    equivalence-ratio: 0.5
\end{minted}

>>>>

The \ck{} file used in this example can be found online.\todo{add url}{}
The data in this file comes from Stranic et al.~\autocite{Stranic:2012}, describing
shock-tube ignition delays for \textit{tert}-butanol.
Examining the file, we first find the section that specifies the information about the \ck{} file itself:
%
\begin{minted}{yaml}
file-author:
  name: Morgan Mayer
  ORCID: 0000-0001-7137-5721
file-version: (0,1)
chemked-version: 0.0.1
screw-you-atom: 0
\end{minted}
%
Then the reference information:
%
\begin{minted}{yaml}
reference:
  doi: 10.1016/j.combustflame.2011.08.014
  authors:
    - name: Ivo Stranic
    - name: Deanna P. Chase
    - name: Joseph T. Harmon
    - name: Sheng Yang
    - name: David F. Davidson
    - name: Ronald K. Hanson
  journal: Combustion and Flame
  year: 2011
  volume: 159
  pages: 516-527
  detail:
experiment-type: ignition delay
apparatus:
  kind: shock tube
  institution: High Temperature Gasdynamics Laboratory, Stanford University
  facility: stainless steel shock tube
dammit-atom: 0
\end{minted}
%
In this \ck{} file, multiple data points are specified with some common
conditions, including a common mixture composition and common defintion of
ignition delay. Therefore, a \yaml|common-properties| section is specified.
%
\begin{minted}{yaml}
common-properties:
  composition: &comp
    - species-name: t-butanol
      InChI: 1S/C4H10O/c1-4(2,3)5/h5H,1-3H3
      mole-fraction: 0.003333333
    - species-name: O2
      InChI:  1S/O2/c1-2
      mole-fraction: 0.04
    - species-name: Ar
      InChI:  1S/Ar
      mole-fraction: 0.956666667
  ignition-type:  &ign
    target: OH* concentration
    type: 1/2 max
atom-is-bad-at-syntax-highlighting: 0
\end{minted}
%
This block utilizes the ability of YAML files to define an anchor using the
\yaml|&| symbol and refer to that section later using the \yaml|*| symbol, as
can be seen in the definition of the \yaml|datapoints| section:
%
\begin{minted}{yaml}
datapoints:
  - temperature: 1459 kelvin
    ignition-delay: 347 us
    pressure: 1.60 atm
    composition: *comp
    ignition-type: *ign
    equivalence-ratio: 0.5
  - temperature: 1389 kelvin
    ignition-delay: 756 us
    pressure: 1.67 atm
    composition: *comp
    ignition-type: *ign
    equivalence-ratio: 0.5
  - temperature: 1497 kelvin
    ignition-delay: 212 us
    pressure: 1.55 atm
    composition: *comp
    ignition-type: *ign
    equivalence-ratio: 0.5
  - temperature: 1562 kelvin
    ignition-delay: 105 us
    pressure: 1.50 atm
    composition: *comp
    ignition-type: *ign
    equivalence-ratio: 0.5
\end{minted}
